### 2015-04-12 approach.tex
Fixing some small notation blips

\subsection{Obtaining the smoothed vector field} \label{sec:getting_vd}
\label{sec:obtainingV}
We define the vector field as $\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1(\vx) \ \upsilon_2(\vx) \ \upsilon_3(\vx)\right]^T$ where $\mathbf{L := [b_1 \ b_2 \ b_3]}$ is a basis for $\realn^3$ that contains the principal lattice directions of the chosen lattice. Each $\upsilon_i$ is a scalar function representing the projection of the smoothed normal field onto each respective principal lattice direction $\mathbf{b}_i$. This may seem unintuitive at first, however, using a non-canonical basis to represent $\vec{V}$ will be convenient in two ways. Firstly, it will allow us to approximate the divergence of $\vec{V}$ by taking directional derivatives of $\vec{V}$ in the principal lattice directions. This is motivated by the fact that it is more natural to approximate derivatives in the principal lattice directions on non-Cartesian lattices. Secondly, it will allow us to construct divergence of the smoothed normal field from more than three principal lattice directions. We also allow each function $\upsilon_i$ to potentially be represented in different function spaces, i.e. {\small 
\begin{equation} 
	\upsilon_i(\vx) = \sum_{k=0}^N \text{v}_ki \varphi_k^i(\vx) \in \aspace{\lattice{L}{\varphi^i}}.
\end{equation}}
The coefficient vector of $\upsilon_i$ is denoted as $\mathbf{v}_i:=\left[\text{v}_1^i \ \cdots \ \text{v}_N^i \right]$.We use the unfortunate notation $\text{v}_j^i, \varphi_k^i$ to denote that those objects belong to $\upsilon_i(x)$, not to denote exponentiation. We consider each component of $\vec{V}(\vx)$ separately, thus, it suffices to describe the process at one $\upsilon_i$. We simply find the $\upsilon_i$ that minimizes {\small 
\begin{equation} \label{eq:vari_eqn}
 	\sump_{\forall (\vx,\vn) \in P }^{M} (\upsilon_i(\vx) - (\mathbf{L}^{-1})_i \cdot \mathbf{n})^2 + E(\upsilon_i).
\end{equation} }
Where $(\mathbf{L}^{-1})_i$ is the $i^{th}$ column of $(\mathbf{L}^{-1}).$ As before, this provides us with a parametrized way of controlling the smoothness of the resulting approximation, without the need to explicitly choose a smoothing kernel. These $\mathbf{v}_i$ can be obtained using the procedure of \SC{sec:vari_review}.

@@

\subsubsection{Four Direction Divergence on the BCC Lattice}
It is also possible to consider a basis $\mathbf{L}$ in which we choose more than three principal directions to reconstruct the divergence. Thus, we may choose $\mathbf{L} = \mathbf{\Xii_{B}} $ as the basis for our function. To accommodate for this, we redefine $\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1 \ \upsilon_2 \ \upsilon_3 \ \upsilon_4 \right.]^T$ Since this matrix is not square, it is not possible to take its inverse in \EQ{eq:vari_eqn}. Instead, the least norm inverse $\mathbf{L^T(LL}^T\mathbf{)}^{-1}$ is used. It is easy to see that, by the same reasoning as in equation \EQ{eq:div_dir}, $\grad \cdot \vec{V} = \dv{\mathbf{b_1}}\upsilon_1 + \dv{\mathbf{b_2}}\upsilon_2 + \dv{\mathbf{b_3}}\upsilon_3 + \dv{\mathbf{b_4}}\upsilon_4$. Thus, we may use the same idea as in the three direction case, approximating each direction separately, and summing the coefficients to obtain an approximation to the divergence (the shifted case is also similar.)
%\begin{equation}
%	\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1 \ \upsilon_2 \ \upsilon_3 \ \upsilon_4 \right.]^T
%\end{equation}

>>>>

\subsection{Obtaining the smoothed vector field} \label{sec:getting_vd}
\label{sec:obtainingV}
We define the vector field as $\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1(\vx) \ \upsilon_2(\vx) \ \upsilon_3(\vx)\right]^T$ where $\mathbf{L := [b_1 \ b_2 \ b_3]}$ is a basis for $\realn^3$ that contains the principal lattice directions of the chosen lattice. Each $\upsilon_i$ is a scalar function representing the projection of the smoothed normal field onto each respective principal lattice direction $\mathbf{b}_i$. This may seem unintuitive at first, however, using a non-canonical basis to represent $\vec{V}$ will be convenient in two ways. Firstly, it will allow us to approximate the divergence of $\vec{V}$ by taking directional derivatives of $\vec{V}$ in the principal lattice directions. This is motivated by the fact that it is more natural to approximate derivatives in the principal lattice directions on non-Cartesian lattices. Secondly, it will allow us to construct divergence of the smoothed normal field from more than three principal lattice directions. We also allow each function $\upsilon_i$ to potentially be represented in different function spaces, i.e. {\small 
\begin{equation} 
	\upsilon_i(\vx) = \sum_{k=0}^N \text{v}_k^i \varphi_k^i(\vx) \in \aspace{\lattice{L}}{\varphi^i}.
\end{equation}}
The coefficient vector of $\upsilon_i$ is denoted as $\mathbf{v}_i:=\left[\text{v}_1^i \ \cdots \ \text{v}_N^i \right]$.We use the unfortunate notation $\text{v}_j^i, \varphi_k^i$ to denote that those objects belong to $\upsilon_i(x)$, not to denote exponentiation. We consider each component of $\vec{V}(\vx)$ separately, thus, it suffices to describe the process at one $\upsilon_i$. We simply find the $\upsilon_i$ that minimizes {\small 
\begin{equation} \label{eq:vari_eqn}
 	\sump_{\forall (\vx,\vn) \in P }^{M} (\upsilon_i(\vx) - (\mathbf{L}^{-1})_i \cdot \vect{n})^2 + E(\upsilon_i).
\end{equation} }
Where $(\mathbf{L}^{-1})_i$ is the $i^{th}$ column of $(\mathbf{L}^{-1}).$ As before, this provides us with a parametrized way of controlling the smoothness of the resulting approximation, without the need to explicitly choose a smoothing kernel. These $\mathbf{v}_i$ can be obtained using the procedure of \SC{sec:vari_review}.

@@

\subsubsection{Four Direction Divergence on the BCC Lattice}
It is also possible to consider a basis $\mathbf{L}$ in which we choose more than three principal directions to reconstruct the divergence. Thus, we may choose $\mathbf{L} = \mathbf{\Xii_{B}} $ as the basis for our function. To accommodate for this, we redefine $\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1 \ \upsilon_2 \ \upsilon_3 \ \upsilon_4 \right.]^T$ Since this matrix is not square, it is not possible to take its inverse in \EQ{eq:vari_eqn}. Instead, the least norm inverse $\mathbf{L^T(LL}^T\mathbf{)}^{-1}$ is used. It is easy to see that, by the same reasoning as in equation \EQ{eq:div_dir}, $\grad \cdot \vec{V} = \dv{\mathbf{b_1}}\upsilon_1 + \dv{\mathbf{b_2}}\upsilon_2 + \dv{\mathbf{b_3}}\upsilon_3 + \dv{\mathbf{b_4}}\upsilon_4$. Thus, we may use the same idea as in the three direction case, approximating each direction separately, and summing the coefficients to obtain an approximation to the divergence (the shifted case is also similar).

### 2015-04-12 prelim.tex
Touching up approach pipeline diagram
Fixing some small notation blips

\section{Preliminaries}\label{sec:pois_review}
\subsection{Poisson Surface Reconstruction}
We denote the indicator function of a model $M$ as $$ \chi_M(\vect{x}) :=
\begin{cases}
1, & \text{if }\vect{x}\text{ is in the interior of the model } M \\
\frac{1}{2}, & \text{if } \vect{x}\text{ is on the model's surface}\\
0, & \text{if }\vect{x}\text{ is exterior to } M
\end{cases}. $$
The key observation of the Poisson surface reconstruction formulation, is that if one obtains a function $\vec{V}(\vect{x})$ with $\vec{V}(\vect{x})\approx{\nabla}\chi_M$, that approximates the smoothed gradient of the indicator function, finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small 
\begin{equation} \label{eq:poisson}
	\lapl{\inda} = {\grad} \cdot \vec{V}.
\end{equation}}
We define the set of input surface points to be $P:=\{(\vect{p}_1,\vect{n}_1), (\vect{p}_2,\vect{n}_2) \hdots (\vect{p}_M,\vect{n}_M) : (\vect{p}_i,\vect{n}_i) \in \realn^3 \times \realn^3 \}$ where $\vect{p}_i$ and $\mathbf{n}_i$ are the position and normal vector of the $i^{th}$ sample respectively. Orientation can be succinctly represented with only two values, however, it is convenient to keep it as the normal at a point, because the length of the normal can be used to encode the sampling density of the point-set at a point. For the following discussion, we also need to introduce the notation $\patch_{\vect{s}}$, which denotes a patch of the surface model about the sample location $\vect{s}$.

>>>>

\section{Preliminaries}
\label{sec:pois_review}
\subsection{Poisson Surface Reconstruction}
We denote the indicator function of a model $M$ as 
$$ \chi_M(\vect{x}) :=
	\begin{cases}
		1, & \text{if }\vect{x}\text{ is in the interior of the model } M \\
		\frac{1}{2}, & \text{if } \vect{x}\text{ is on the model's surface} \\
		0, & \text{if }\vect{x}\text{ is exterior to } M
	\end{cases}. 
$$.
The key observation of the Poisson surface reconstruction formulation, is that if one obtains a function $\vec{V}(\vect{x})$ with $\vec{V}(\vect{x})\approx{\nabla}\chi_M$, that approximates the smoothed gradient of the indicator function, finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small 
\begin{equation} \label{eq:poisson}
	\lapl{\inda} = {\grad} \cdot \vec{V}.
\end{equation}}
We define the set of input surface points to be $P:=\{(\vect{p}_1,\vect{n}_1), (\vect{p}_2,\vect{n}_2) \hdots (\vect{p}_M,\vect{n}_M) : (\vect{p}_i,\vect{n}_i) \in \realn^3 \times \realn^3 \}$ where $\vect{p}_i$ and $\mathbf{n}_i$ are the position and normal vector of the $i^{th}$ sample respectively. Orientation can be succinctly represented with only two values, however, it is convenient to keep it as the normal at a point, because the length of the normal can be used to encode the sampling density of the point-set at a point. For the following discussion, we also need to introduce the notation $\patch_{\vect{s}}$, which denotes a patch of the surface model about the sample location $\vect{s}$.
